```{r}
#| label: setup
#| include: false

library(here)

here("R", ".setup.R") |> source()
```

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![License: GPLv3](https://img.shields.io/badge/license-GPLv3-bd0000.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![License: CC BY-NC-SA 4.0](https://img.shields.io/badge/license-CC_BY--NC--SA_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by-nc-sa/4.0/)
[![Contributor Covenant 3.0 code of conduct badge](https://img.shields.io/badge/Contributor%20Covenant-3.0-4baaaa.svg)](https://www.contributor-covenant.org/version/3/0/code_of_conduct/)
<!-- badges: end -->

## Overview

## `brand.yml` Configuration

<!-- %:::% brand.yml begin %:::% -->
``` {.yml filename="brand.yml"}
meta:
  name:
    short: PPSP
    full: Pizzonia's Personal Study Project
  link:
    github: https://github.com/marciopizzonia
    linkedin: https://www.linkedin.com/in/marcio-antonio-pizzonia-junior-b64798305/
  description: |
    The Pizzonia's Personal Study Project (PPSP) was created to investigate questions and topics that go beyond the scope of formal academic coursework, fostering independent learning and intellectual exploration.
  founded: 2026

color:
  palette:
    black: "#141414"
    dark-red: "#8b0000"
    orange: "#eb4c00" 
    blue: "#0078b4"
    white: "#ffffff"
    gray: "#868489"
    mono-orange-1: "#ffedeb" 
    mono-orange-2: "#ffc1ba"
    mono-orange-3: "#ff8672"
    mono-orange-4: "#ae3600"
    mono-orange-5: "#752100"
    mono-orange-6: "#400e00"
    comp-orange-1: "#d3e7ff" 
    comp-orange-2: "#81c3ff"
    comp-orange-3: "#009feb"
    comp-orange-4: "#00547f"
    comp-orange-5: "#00324e"
    comp-orange-6: "#001321"
    square-purple: "#3f0074"
    square-green: "#9ffe00"
    square-blue: "#08ffe3"
    square-red: "#a80013"
    gray-l50: "#c1bfc4" 
    gray-l75: "#b9b9b9"
    gray-l90: "#e2e2e2"
    gray-l95: "#f1f1f1"
  background: white
  primary: orange
  secondary: blue
  tertiary: black
  success: square-green
  info: square-blue
  warning: mono-orange-3
  danger: dark-red
  light: white
  dark: black

typography:
  fonts:
    - family: Montserrat
      source: google
    - family: Roboto
      source: google
    - family: Roboto Mono
      source: google
  base:
    family: Roboto
    line-height: 1.5
    weight: normal
  headings:
    family: Montserrat
    color: orange
    line-height: 1.25
    weight: 800
  monospace: Roboto Mono
  monospace-inline:
    color: comp-orange-4
    background-color: gray-l95
  monospace-block:
    background-color: gray-l95
  link:
    color: comp-orange-4
    decoration: none
```
<!-- %:::% brand.yml end %:::% -->

## Set the Environment

### Load Packages

```{r}
#| code-fold: false
#| output: false

library(brandr)
library(dplyr)
library(geobr)
library(ggplot2)
library(ggspatial)
library(here)
library(htmltools)
library(palmerpenguins)
library(sf)
library(tidyr)
```

## Bar Plots

```{r}
penguins |>
  ggplot(
    aes(
      x = sex,
      fill = species
    )
  ) +
  geom_bar(alpha = 0.8) +
  facet_wrap(vars(species), ncol = 1) +
  scale_fill_brand_d() +
  coord_flip() +
  labs(
    x = "Island",
    y = "Frequency",
    fill = "Species"
  )
```

## Histograms

```{r}
penguins |>
  drop_na(
    flipper_length_mm,
    species
  ) |>
  ggplot(
    aes(
      x = flipper_length_mm,
      fill = species
    )
  ) +
  geom_histogram(
    bins = 30,
    alpha = 0.5,
    position = "identity"
  ) +
  scale_fill_brand_d() +
  labs(
    x = "Flipper Length (mm)",
    y = "Frequency",
    fill = "Species"
  )
```

## Boxplots

```{r}
penguins |>
  drop_na(
    bill_length_mm,
    species
  ) |>
  ggplot(
    aes(
      x = species,
      y = bill_length_mm,
      fill = species
    )
  ) +
  geom_boxplot(
    outlier.color = get_brand_color("dark-red")
  ) +
  geom_jitter(
    width = 0.2,
    alpha = 0.1
  ) +
  scale_fill_brand_d(alpha = 0.7) +
  labs(
    x = "Species",
    y = "Bill Length (mm)",
    fill = "Species"
  )
```

## Density

```{r}
penguins |>
  drop_na(
    flipper_length_mm,
    species
  ) |>
  ggplot(
    aes(
      x = flipper_length_mm,
      fill = species
    )
  ) +
  geom_density(
    alpha = 0.5,
    position = "identity"
  ) +
  scale_fill_brand_d() +
  labs(
    x = "Flipper Length (mm)",
    y = "Density",
    fill = "Species"
  ) +
  theme(
    legend.position = "none"
  )
```

## Scatterplots

```{r}
penguins |>
  drop_na(
    body_mass_g,
    flipper_length_mm,
    species
  ) |>
  ggplot(
    aes(
      x = body_mass_g,
      y = flipper_length_mm,
      color = species,
      shape = species
    )
  ) +
  geom_point(size = 2) +
  geom_smooth(
    method = "lm",
    formula = y ~ x,
    se = FALSE
  ) +
  scale_color_brand_d(alpha = 0.7) +
  labs(
    x = "Body Mass (g)",
    y = "Flipper Length (mm)",
    color = "Species",
    shape = "Species"
  )
```

## Maps

```{r}
#| output: false

brazil_states <- read_state(year = 2024)
```

```{r}
#| output: false

data <-
  brazil_states |>
  mutate(
    n = sample(
      1:1000,
      size = n(),
      replace = TRUE
    ),
  )
```

```{r}
plot <-
  data |>
  ggplot() +
  geom_sf(
    aes(fill = n),
    color = get_brand_color("gray")
  ) +
  scale_fill_brand_b(
    n.breaks = 6
  ) +
  labs(fill = NULL) +
  annotation_scale(
    location = "br",
    style = "tick",
    width_hint = 0.25,
    height = unit(0.15, "cm")
  ) +
  annotation_north_arrow(
    location = "br",
    height = unit(2, "lines"),
    width = unit(2, "lines"),
    pad_x = unit(0.25, "lines"),
    pad_y = unit(1.25, "lines"),
    style = north_arrow_fancy_orienteering
  )
```

### Continuous

```{r}
#| messages: false
#| #| warning: false

plot
```

### Diverging

```{r}
#| messages: false
#| #| warning: false

plot +
  scale_fill_brand_b(
    color_type = "div",
    n.breaks = 6
  )
```

## License

::: {style="text-align: left;"}
[![License: GPLv3](https://img.shields.io/badge/license-GPLv3-bd0000.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![License: CC BY-NC-SA 4.0](https://img.shields.io/badge/license-CC_BY--NC--SA_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by-nc-sa/4.0/)
:::

The code in this report is licensed under the [GNU General Public License Version 3](https://www.gnu.org/licenses/gpl-3.0), while the report is available under the [Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International](https://creativecommons.org/licenses/by-nc-sa/4.0/) license.

``` text
Copyright (C) 2026 Pizzonia's Personal Study Project

The code in this report is free software: you can redistribute it and/or
modify it under the terms of the GNU General Public License as published by the
Free Software Foundation, either version 3 of the License, or (at your option)
any later version.

This program is distributed in the hope that it will be useful, but WITHOUT ANY
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
PARTICULAR PURPOSE. See the GNU General Public License for more details.

You should have received a copy of the GNU General Public License along with
this program. If not, see <https://www.gnu.org/licenses/>.
```
