```{r}
#| label: setup
#| include: false

library(here)

here("R", ".setup.R") |> source()
```

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![License: GPLv3](https://img.shields.io/badge/license-GPLv3-bd0000.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![License: CC BY-NC-SA 4.0](https://img.shields.io/badge/license-CC_BY--NC--SA_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by-nc-sa/4.0/)
[![Contributor Covenant 3.0 code of conduct badge](https://img.shields.io/badge/Contributor%20Covenant-3.0-4baaaa.svg)](https://www.contributor-covenant.org/version/3/0/code_of_conduct/)
<!-- badges: end -->

# Overview

This repository showcases the visual style of the projects I aim to develop for educational purposes. Furthermore, it serves as a learning resource for my personal development and demonstrates the application of the [`brand.yml`](https://posit-dev.github.io/brand-yml/) configuration.

The report is available [here](https://github.com/marciopizzonia/visual-style).

# `_brand.yml` Configuration

<!-- %:::% brand.yml begin %:::% -->
``` {.yml filename="brand.yml"}
meta:
  name:
    short: PPSP
    full: Pizzonia's Personal Study Project
  link:
    github: https://github.com/marciopizzonia
    linkedin: https://www.linkedin.com/in/marcio-antonio-pizzonia-junior-b64798305/
  description: |
    The Pizzonia's Personal Study Project (PPSP) was created to investigate questions and topics that go beyond the scope of formal academic coursework, fostering independent learning and intellectual exploration.
  founded: 2026

color:
  palette:
    black: "#141414"
    dark-red: "#8b0000"
    orange: "#eb4c00" 
    blue: "#0078b4"
    white: "#ffffff"
    gray: "#868489"
    mono-orange-1: "#ffedeb" 
    mono-orange-2: "#ffc1ba"
    mono-orange-3: "#ff8672"
    mono-orange-4: "#ae3600"
    mono-orange-5: "#752100"
    mono-orange-6: "#400e00"
    comp-orange-1: "#d3e7ff" 
    comp-orange-2: "#81c3ff"
    comp-orange-3: "#009feb"
    comp-orange-4: "#00547f"
    comp-orange-5: "#00324e"
    comp-orange-6: "#001321"
    square-purple: "#3f0074"
    square-green: "#9ffe00"
    square-blue: "#08ffe3"
    square-red: "#a80013"
    gray-l50: "#c1bfc4" 
    gray-l75: "#b9b9b9"
    gray-l90: "#e2e2e2"
    gray-l95: "#f1f1f1"
  background: white
  primary: orange
  secondary: blue
  tertiary: black
  success: square-green
  info: square-blue
  warning: mono-orange-3
  danger: dark-red
  light: white
  dark: black

typography:
  fonts:
    - family: Montserrat
      source: google
    - family: Roboto
      source: google
    - family: Roboto Mono
      source: google
  base:
    family: Roboto
    line-height: 1.5
    weight: normal
  headings:
    family: Montserrat
    color: orange
    line-height: 1.25
    weight: 800
  monospace: Roboto Mono
  monospace-inline:
    color: comp-orange-4
    background-color: gray-l95
  monospace-block:
    background-color: gray-l95
  link:
    color: comp-orange-4
    decoration: none
```
<!-- %:::% brand.yml end %:::% -->

# Set the Environment

## Load Packages

```{r}
#| code-fold: false
#| output: false

library(brandr)
library(dplyr)
library(geobr)
library(ggplot2)
library(ggspatial)
library(here)
library(htmltools)
library(palmerpenguins)
library(sf)
library(tidyr)
```

# Charts

## Comparison

### Static

#### One Variable: Single Bar Chart

#### Two Variables: Viariable Widht Column Chart

#### Three or More Variables

##### Few Items: Multiple Bar Charts

##### Many Items: Table With Embedded Charts

### Changing Over Time

#### Many Periods

##### Cyclical Data: Circular Area Chart

##### Noncyclical Data: Line Chart

#### Few Periods

##### Single or Few Items: Column Chart

##### Many Items: Line Chart

## Distribution 

### Single Variable

#### Few Items: Column Histogram

#### Many Items: Line Histogram

### Two Variables: Scatter Chart

### Three Variables: 3D Area Chart

## Composition

### Changin Over Time

#### Few Periods

##### Only Relative Differences Matter: Stacked 100% Column Chart

##### Relative and Absolute Differences Matter: Stacked Column Chart

#### Many Periods

##### Only Relative Differences Matter: Stacked 100% Area Chart

##### Relative and Absolute Differences Matter: Stacked Area Chart

### Static

#### Simple Share of Total: Pie Chart

#### Accumulation or Subtraction to Total: Waterfall Chart

#### Components of Components: Stacked 100% Column Chart With Subcomponents

## Relationship

### Two Variables: Scatter Chart

### Three Variables: Bubble Chart

# Maps

## Distribution

### Discrete: Dot Map

1 dot = 1 unit

### Continuous: Heatmap

Color = Density

## Quantity 

### By Region: Choropleth

Color = Intenisty

### By Point: Proportional Symbol

Size = Value

## Location

### Simple: Marker Map

Pin = 1 Place

### Categorical: Categorical Icons

1 icon = category

## Flow

### Origin to Destination: Flow Map

Width = Volume

### Continuous: Route Track

GPS/Rout Path

## Comparsion

### Distortion: Cartogram

Propotional area to the value

### Keep Shape: Isochrone

Time Rings

## Special Cases & Combinations

### Multiple Variables: Bivariant Map or Combined Map

### Terrain/Relief: Hillshade/Contour/3D

### Network/Connection: Geospatial Map (node-link map)

### Temporal Data: Animated Map


## License

::: {style="text-align: left;"}
[![License: GPLv3](https://img.shields.io/badge/license-GPLv3-bd0000.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![License: CC BY-NC-SA 4.0](https://img.shields.io/badge/license-CC_BY--NC--SA_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by-nc-sa/4.0/)
:::

The code in this report is licensed under the [GNU General Public License Version 3](https://www.gnu.org/licenses/gpl-3.0), while the report is available under the [Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International](https://creativecommons.org/licenses/by-nc-sa/4.0/) license.

``` text
Copyright (C) 2026 Pizzonia's Personal Study Project

The code in this report is free software: you can redistribute it and/or
modify it under the terms of the GNU General Public License as published by the
Free Software Foundation, either version 3 of the License, or (at your option)
any later version.

This program is distributed in the hope that it will be useful, but WITHOUT ANY
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
PARTICULAR PURPOSE. See the GNU General Public License for more details.

You should have received a copy of the GNU General Public License along with
this program. If not, see <https://www.gnu.org/licenses/>.
```

## References {.unnumbered}

::: {#refs}
:::
